\cvsection{Professional Experience}

\begin{cventries}
\vspace{-4mm}
\cventry
  {Project Manager}
  {Hundsun Technologies}
  {Hangzhou, China}
  {Aug. 2021 – May. 2023}
  {
    \begin{cvitems}
        \item {Led enterprise Fund Transfer System migration (TA4 → TA6) for CITIC Securities, delivering a zero-downtime upgrade for critical financial infrastructure.}
        \item {Managed a cross-functional engineering team of 10+ members using Agile methodology, coordinating sprint planning and release delivery.}
        \item {Implemented proactive risk mitigation and issue resolution processes during system deployment.}
        \item {Redesigned system workflows and architecture, improving operational efficiency by 25\%.}
    \end{cvitems}
  }
\vspace{4mm}
\cventry
  {Operations Manager}
  {Khorgas International Port Logistics}
  {Khorgas, China}
  {May. 2023 – Dec. 2024}
  {
    \begin{cvitems}
        \item {Directed cross-border logistics operations managing a workforce of 50 employees and heavy-equipment fleet.}
        \item {Maintained daily cargo throughput exceeding 120 tons in a high-volume logistics environment.}
        \item {Identified operational bottlenecks and redesigned workflows to improve operational efficiency.}
        \item {Enforced Environmental Health \& Safety (EHS) compliance, achieving zero operational incidents.}
    \end{cvitems}
  }
\vspace{4mm}
\cventry
  {Administrative Project Coordinator}
  {Xiaolan Town Government}
  {Zhongshan, China}
  {Jan. 2025 – Jul. 2025}
  {
    \begin{cvitems}
        \item {Coordinated cross-departmental operations for a public event with over 10,000 attendees.}
        \item {Collaborated with municipal departments and external stakeholders to ensure seamless execution.}
        \item {Improved administrative workflows and communication processes across departments.}
    \end{cvitems}
  }
\end{cventries}